
\begin{thebibliography}{9}
\bibitem{ICAO} 
International Civil Aviation Organization.
\textit{DOC 9303, Machine Readable Travel Documents.} Seventh Edition. International Civil Aviation Organization, 2015.

\bibitem{ICAO_2} 
Internation Civil Aviation Organization. 
\textit{Cryptography 101, Basics of ePassport secuirty}.
Internation Civil Aviation Organization. \\
\url{https://www.icao.int/Security/FAL/PKD/BVRT/Pages/Basics.aspx} (accessed 5.10.2020).

\bibitem{OAEP} 
Wikipedia.
\textit{Optimal Encryption Padding}. Wikipedia\\
\url{https://en.wikipedia.org/wiki Optimal_asymmetric_encryption_padding} (accessed 7.10.2020, last updated: 21 January 2020, at 12:19)

\bibitem{Read_id} 
READID.  
\textit{Cloning detection for ePassports}.
READID. \\
\url{https://readid.com/blog/Cloning-detection-for-ePassports} (accessed 3.10.2020, published Feb 21, 2018, last updated: Updated 22 oct 2019 with status PACE).

\bibitem{PKI} 
Wikipedia.  
\textit{Public Key Infrastructure}.
Wikipedia. \\
\url{https://en.wikipedia.org/wiki/Public_key_infrastructure} (accessed 8.10.2020,  last updated: 20 September 2020, at 18:22).

\bibitem{SafeNet} 
SafeNet.  
\textit{E-Passport: Deploying Hardware Security Modules to Ensure Data Authenticity and Integrity for Electronic Passport Projects}.
SafeNet. \\
\url{https://www.slideshare.net/SafeNet/epassport-deploying-hardware-security-modules-to-ensure-data-authenticity-and-integrity-for-electronic-passport-projects} (accessed 9.10.2020,  Published: on Jun 10, 2011).

\bibitem{ICAO_3} 
International Civil Aviation Organization.
\textit{DOC 9303, Machine Readable Travel Documents, Part 9.} Seventh Edition. International Civil Aviation Organization. p.36, 2015.

\bibitem{ICAO_4} 
International Civil Aviation Organization.
\textit{Member States.} International Civil Aviation Organization.\\
\url{https://www.icao.int/about-icao/pages/member-states.aspx} (accessed 21.10.2020)

\bibitem{ICAO_5} 
International Civil Aviation Organization.
\textit{Document Signer.} International Civil Aviation Organization.\\
\url{https://www.icao.int/Security/FAL/PKD/BVRT/Pages/DS.aspx} (accessed 21.10.2020)

\end{thebibliography}